Etox-Base: A tool to derive exposure endpoints from chemical test results

### 2019-02-09 article/tikz/pipeline_organigram.tex

	%% chemicals and organisms
	\begin{scope}[local bounding box = query]
	\node (cas) [ids, below of=io, yshift = -2.5cm, xshift = 3cm] {CAS};
	% main nodes
	\node (chemscr) [main, right of=cas, xshift=4.5cm] {PHYS-CHEM}
    	child { node [children] { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
    	child { node [children] { Pesticide Action Network - \textbf{qu\_pan.R} }}
    	child { node [children] { PhysProp - \textbf{qu\_pp.R} }}
    	child { node [children] { PubChem - \textbf{qu\_pubchem.R} }};
	\node (taxon) [ids, below of=cas, yshift=-6cm, align = center] {Taxon};
	% main nodes
	\node (habitat) [main, right of = taxon, xshift = 4.5cm, yshift = 1.5cm] {Habitats}
    	child { node [children] { WORMS data base - \textbf{qu\_worms.R} }}
    	child { node [children] { Manual Search - \textbf{qu\_manual.R} }};
	\node (region) [main, right of = taxon, xshift = 4.5cm, yshift = -1.5cm] {Regions}
	    child { node [children] { GBIF - \textbf{qu\_gbif.R} }};
	\end{scope}
	% bbox
	\begin{pgfonlayer}{bg3}
	\node (back_query) [background, minimum height=12cm, above of=cas, xshift=7cm, yshift=-5.5cm];
	\node (back_query_label) [right of = back_query, xshift = 11.5cm, rotate = 90]
	    {\huge{Query scripts}};
	\end{pgfonlayer}

	%% result
	\node (testres) [main, right of = cas, xshift = 14cm, yshift = -13cm] {Merge}
	    child { node [children]  { \textbf{re\_merge.R} }}
	    child { node [children]  { \textbf{re\_combine.R} }};
	\node (analysesres) [main, left of = testres, xshift = -4.5cm] {Analyses}
	    child { node [children]  { \textbf{re\_analyses.R} }};
	\node (checksres) [main, left of = analysesres, xshift = -4.5cm] {checks}
	    child { node [children]  { \textbf{re\_checks.R} }};
	\node (finalres) [main, left of = checksres, xshift = -4.5cm] {Final Table}
	    child { node [children]  { \textbf{re\_final.R} }};
	% bbox
	\begin{pgfonlayer}{bg3}
	\node (back_result) [background, minimum height=4cm, above of=finalres, xshift=8.5cm, yshift=-1cm];
	\node (back_result_label) [right of = back_result, xshift = 11.5cm, rotate = 90, align = center]
	    {\huge{Result}\\\huge{scripts}};
	\end{pgfonlayer}

>>>>

	%% chemicals and organisms
	\begin{scope}[local bounding box = query]
	\node (cas) [ids, below of=io, yshift = -2.5cm, xshift = 3cm] {CAS};
	% main nodes
	\node (chemscr) [main, right of=cas, xshift=4.5cm] {PHYS-CHEM}
    	child { node [children] { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
    	child { node [children] { Chemspider - \textbf{qu\_chemspider\_scrape.R } }}
    	child { node [children] { Eurostat - \textbf{qu\_eurostat\_chem\_class.R} }}
    	child { node [children] { PubChem - \textbf{qu\_pc.R} }}
    	child { node [children] { PhysProp - \textbf{qu\_pp.R} }};
	\node (taxon) [ids, below of=cas, yshift=-6cm, align = center] {Taxon};
	% main nodes
	\node (habitat) [main, right of = taxon, xshift = 4.5cm, yshift = 1.5cm] {Habitats}
    	child { node [children] { WORMS data base - \textbf{qu\_worms2.R} }};
	\node (region) [main, right of = taxon, xshift = 4.5cm, yshift = -1.5cm] {Regions}
	    child { node [children] { GBIF - \textbf{qu\_gbif.R} }};
	\end{scope}
	% bbox
	\begin{pgfonlayer}{bg3}
	\node (back_query) [background, minimum height=12cm, above of=cas, xshift=7cm, yshift=-5.5cm];
	\node (back_query_label) [right of = back_query, xshift = 11.5cm, rotate = 90]
	    {\huge{Query scripts}};
	\end{pgfonlayer}

	%% result
	\node (testres) [main, right of = cas, xshift = 14cm, yshift = -13cm] {Merge}
	    child { node [children]  { \textbf{re\_merge.R} }}
	    child { node [children]  { \textbf{re\_combine.R} }};
	\node (analysesres) [main, left of = testres, xshift = -4.5cm] {Analyses}
	    child { node [children]  { \textbf{re\_analyses.R} }};
	\node (checksres) [main, left of = analysesres, xshift = -4.5cm] {checks}
	    child { node [children]  { \textbf{re\_checks\_internal.R} }};
	\node (finalres) [main, left of = checksres, xshift = -4.5cm] {Final Table}
	    child { node [children]  { \textbf{re\_final.R} }};
	% bbox
	\begin{pgfonlayer}{bg3}
	\node (back_result) [background, minimum height=4cm, above of=finalres, xshift=8.5cm, yshift=-1cm];
	\node (back_result_label) [right of = back_result, xshift = 11.5cm, rotate = 90, align = center]
	    {\huge{Result}\\\huge{scripts}};
	\end{pgfonlayer}
